pema application

### 2022-12-05 paper/action_letter.Rmd
fixed typos

We recognize that this choice of words was confusing.
The regularizing horseshoe prior is an extension of the horseshoe prior.
To address this comment, we now explain this in the text:

@@

We thank the Reviewer for pointing this out;
a fragment of a sentance was cut here.
We restored the original text.

>>>>

We recognize that this choice of words was confusing.
The regularized horseshoe prior is an extension of the horseshoe prior.
To address this comment, we now explain this in the text:

@@

We thank the Reviewer for pointing this out;
a fragment of a sentence was cut here.
We restored the original text.
